
The original creators of WolfTutor proposed three additional features for future development. The first was to integrate an online platform to conduct tutoring sessions online. The second was to allow both the tutor and the student to sync their session reservation with their calendar, e.g. Google Calendar. Lastly, to update the scheduling algorithm such that a user could edit or delete reservations in addition to being able to create and view them. Our team provided two other features as well: increasing matching options between tutors and students and allowing students to browse their reservation history. 

\subsection{Pain Points}
\label{sec:pain-points}
After careful consideration, three main pain points were decided upon that consisted of the proposed enhancements. Integration of an online platform was discarded because it was not thought to facilitate the quality of the match between tutor and student.

\paragraph{Scheduling and Calendar Sync}
WolfTutor currently only allows users seeking a tutoring session to create and view reservations. In real life, people change their mind or events come up such that a schedule change is in order. The ability to cancel or reschedule reservations would make WolfTutor more applicable to real world scheduling scenarios. In addition, facilitating intergration with commonly used calendars such as Google and IOS Calendar extends this principle of making scheduling easier.

\paragraph{Increasing Matching Options}
In regards to matching with tutors, WolfTutor currently displays a list of tutor's and their ratings based on the student's desired subject. Then, the student may attempt to book a reservation with a tutor they choose. By expanding matching options, a student should be able easily find a higher quality match with a tutor. For example, a student could filter tutors by location by selecting only locations they want to meet up at in a checkbox. Similarily, if a student has a few tutors they prefer, they could select those names from a checkbox such that WolfTutor only displays those tutors. This type of filtering system is often used by medical facilities with multiple practioners and multiple practing sites. It is also used by NC State University's scheduling tool on epack.

\paragraph{History and Recommendations}
WolfTutor does currently allow for student's to review and rate the tutors that they met with previously. However, there is no way to view a student's reservation history past the most recent tutor. WolfTutor also does not provide a way for a student to easily re-book a new reserveration with a tutor they chose previously if they liked the tutor and would like to schedule a reservation with them again. Adding these enhancements would increase ease of use by helping a student distinguish between a competent and non-competent tutor they've had in the past. 

\subsection{Initial Study}
\label{sec:initial-study}

\subsection{Chosen Enhancement}
\label{sec:chosen-enhancement}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../../main"
%%% End:
